%
Fingerprint pattern classification is a well studied field and there are many works reported in literatures.  An overview of some related work follows.
%
Karu and Jain \cite{karuJain1996} presented a rule-based classifier based on extracting singular points. 
%
Fitz and Green \cite{FitzGreen1996} used a Hexagonal Fourier Transform to classify fingerprints into whorls, loops and arches. 
%
Jain \textit{et al.} \cite{JainSalil1999} used a bank of Gabor filters to compute a feature vector (FingerCode) and then used a K-nearest neighbor classifier and a set of neural networks to classify a feature vector into one of the five fingerprint pattern classes.
%
Cappelli \textit{et al.} \cite{cappelli1999} partitioned a fingerprint directional image into ``homogeneous'' connected regions according to the fingerprint topology, resulting in a synthetic representation which is then used as a basis for the classification.
%
Bernard \textit{et al.} \cite{Bernard2001} used the Kohonen topologic map for fingerprint pattern classification. 
%
Kai Cao \textit{et al.}\cite{cao2013fingerprint} proposed to extract fingerprint orientation feature and used a hierarchical classifier for classification.
%
Ruxin Wang \textit{et al.} \cite{wang2014fingerprint} also used orientation filed as features. %By adopting a stacked autoencoder, they achieved 93.1\% in four-class classification.
%%


Previous works mostly consist of singularity points (core and delta) detection or extracting features such as ridge and orientation flow, or using human markups (or handcrafted features) as the basis for pattern type classification. 
%
Therefore, the accuracy of these methods depends on the goodness (or utility) of the selected features and the precision of the feature extraction portion of the pattern classification algorithms. Both are sensitive to the noise and the variations of the gray-scale level of the input image.  
%
Using handcrafted features can improve performance.  However, in addition to being burdensome and time consuming, accuracy of handcrafted features cannot be guaranteed due to the existence of noise and poor image quality. 
%
Their repeatability and reproducibility cannot be guaranteed either, due to inter- and intra-examiners variations \cite{fbiBlackbox}.  
%
Our approach differs from the previous works in the sense that we use fingerprint images instead of features as input. Convolutional neural network (CNN) has the capability of learning features and it can be directly applied on raw images. CNN exhibits powerful classification capability in many areas\cite{lecun2015deep}\cite{szegedy2016rethinking}.
%
Different from common CNN-based approach, we employ a Support Vector Machine (SVM) on top of deep ConvNet as classifier for prediction.


